Hydrodynamics and rheology of a vesicle doublet suspension

### 2019-07-09 vesicle_code/docs/adhesion/adhesion.tex
updated font size in new figure 6
working on shear revisions

Figure~\ref{fig:doublet090} shows snapshots of two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  The two vesicles are identical with reduced area $\Delta A =
0.9$, shear rate $\chi = 0.5$, separation distance $\delta = 0.4$, and
Hamaker constant $\mathcal{H} = 0.7$.  The vesicles in the doublet move
in tandem rather than performing the tank-treading motion that is
observed in the absence of adhesion.  Similar to the quiescent example,
the membrane tension is negative in the contact region indicating that
the membrane is being compressed when the adhesive force is strongest.

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090} The formation of a doublet in a shear
  flow.  The reduced area is $\Delta A = 0.9$, the Hamaker constant is
  $\mathcal{H}=0.7$, the separation distance is $\delta = 0.4$, and the
  shear rate is $\chi=0.5$.}
\end{figure}

@@

In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
doublet to make a complete revolution at a variety of Hamaker constants
and shear rates.  For a fixed Hamaker constant, as expected, the period
decreases for larger shear rates.  In addition, for a fixed shear rate,
the period decreases as the Hamaker constant increases, but the period
eventually plateaus.  The dynamics of these doublet have similar
behavior to a single rigid body undergoing a Jeffery orbit in a shear
flow.  Therefore, we define the effective aspect ratio
$\lambda_{\mathrm{eff}}$ which satisfies
\begin{align*}
  \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right) = p,
\end{align*}
where $p$ is the period of the doublet.  The effective aspect ratio is
the aspect ratio of an ellipse in a shear flow that is undergoing a
Jeffery orbit with period $p$.  For the Hamaker constant $\mathcal{H} =
2$, the shear rates, periods, and effective aspect ratio are summarized
in Table~\ref{tbl:aspectRatio}.  Since the effective aspect ratio is
comparable for all three shear rates, this indicates that the dynamics
of a vesicle doublet in a shear flow resembles a rigid body undergoing a
Jeffery orbit.
\begin{table}[htp]
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 38.06 & 2.92 \\
  0.75 & 24.81 & 2.85 \\
  1.00 & 19.47 & 3.00 
\end{tabular}
\todo[inline]{Update these values with new periods.  Maybe need to
consider more than one Hamaker constant}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
Hamaker constant $\mathcal{H} = 2$, and separation distance $\delta =
0.4$.  The effective aspect ratios are comparable for all three shear
rates.}
\end{table}

>>>>

Figures~\ref{fig:doublet090-weakAdhesion}
and~\ref{fig:doublet090-strongAdhesion} show snapshots of two vesicles
that have formed a doublet and the color coding is the tension along the
vesicle.  The two vesicles are identical with reduced area $\Delta A =
0.9$, shear rate $\chi = 0.5$, separation distance $\delta = 0.4$, and
Hamaker constant $\mathcal{H} = 0.7$
(Figure~\ref{fig:doublet090-weakAdhesion}) and $\mathcal{H} = 2.1$
(Figure~\ref{fig:doublet090-strongAdhesion}).  The vesicles in the
doublet move in tandem rather than performing the tank-treading motion
that is observed in the absence of adhesion.  Similar to the quiescent
example, the membrane tension is negative in the contact region
indicating that the membrane is being compressed when the adhesive force
is strongest.

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS7em1Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090-weakAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=0.7$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

\begin{figure}[htp]
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image01.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image02.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image03.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image04.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image05.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image06.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image07.png}
  \includegraphics[width=0.24\textwidth]{figs/adR4em1adS2p1e0Chi5em1_ra090_image08.png}
  \caption{\label{fig:doublet090-strongAdhesion} The formation of a
  doublet in a shear flow.  The reduced area is $\Delta A = 0.9$, the
  Hamaker constant is $\mathcal{H}=2.1$, the separation distance is
  $\delta = 0.4$, and the shear rate is $\chi=0.5$.}
\end{figure}

@@

In Figure~\ref{fig:sflow_distance}(b), we plot the time required for the
doublet to make a complete revolution at a variety of Hamaker constants
and shear rates.  For a fixed Hamaker constant, as expected, the period
decreases for larger shear rates.  In addition, for a fixed shear rate,
the period decreases as the Hamaker constant increases, but the period
eventually plateaus.  The dynamics of these doublet have similar
behavior to a single rigid body undergoing a Jeffery orbit in a shear
flow.  Therefore, we define the effective aspect ratio
$\lambda_{\mathrm{eff}}$ which satisfies
\begin{align*}
  \frac{2\pi}{\chi}\left(\lambda + \lambda^{-1} \right) = p,
\end{align*}
where $p$ is the period of the doublet.  The effective aspect ratio is
the aspect ratio of an ellipse in a shear flow that is undergoing a
Jeffery orbit with period $p$.  For the Hamaker constant $\mathcal{H} =
2$, the shear rates, periods, and effective aspect ratio are summarized
in Table~\ref{tbl:aspectRatio}.  Since the effective aspect ratio is
comparable for all three shear rates, this indicates that the dynamics
of a vesicle doublet in a shear flow resembles a rigid body undergoing a
Jeffery orbit.
\begin{table}[htp]
  \begin{tabular}{>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}
>{\centering\arraybackslash}p{2cm}}
  $\chi$ & $p$ & $\lambda_{\mathrm{eff}}$ \\
  \hline
  0.50 & 38.06 & 2.92 \\
  0.75 & 24.81 & 2.85 \\
  1.00 & 19.47 & 3.00 
\end{tabular}
\todo[inline]{Update these values with new periods.  Maybe need to
consider more than one Hamaker constant}
\caption{\label{tbl:aspectRatio} The shear rate, period, and effective
aspect ratio of a vesicle doublet with reduced area $\Delta A = 0.9$,
Hamaker constant $\mathcal{H} = 2$, and separation distance $\delta =
0.4$.  The effective aspect ratios are comparable for all three shear
rates.}
\end{table}
\todo[inline]{period results with $\delta$ = 0.1, 0.2, 0.3, 0.4 so that
we can simply say how it affects the period}
